### 2014-10-01 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add details to results and discussion sections related to flow path, hazard, and tactics; add abstract and summary

% The spread of fire and hot gases into the second floor of the structure was limited by a closed steel-faced, wood-framed door. After exposure to the elevated temperatures and pressure from the fire in the porch area, the wood frame of the door decomposed, the steel faces of the door failed, and the door collapsed inward. The door failure resulted in the establishment of a flow path between the higher pressure and higher temperature conditions in the enclosed porch and the lower pressure and lower temperature conditions in the hallway and kitchen areas of the second floor. The temperature of the gases that flowed into the hallway exceeded 260~$^{\circ}$C (500~$^{\circ}$F) at a height of 1.86~m (6~ft). Unfortunately, a captain and firefighter were advancing a hose line in the hallway near the door at the time of the door failure. It appears that the captain was likely overcome by the rapid change in conditions before he could exit to the safety of the kitchen area. After a Mayday call, the captain was rescued from the structure, but later succumbed to his injuries.

@@

Part of the function of the Fire Research Division at the National Institute of Standars and Technology (NIST) is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response. NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas,Weinschenk:Chicago}. The objective of these studies has been to improve the safety and effectiveness of firefighters.

@@

In Fig.~\ref{fig:hrr_w_fds}, the solid line represents the HRR that was prescribed in the FDS simulation, and the dashed line represents the actual HRR that was predicted by FDS based on the ventilation conditions. From 0~s to 300~s, the predicted HRR was in agreement with the prescribed HRR because there was an adequate amount of oxygen for all of the fuel to combust. From 300~s to 342~s (the time at which the first basement window failed), the predicted HRR was lower than the prescribed HRR because the fire conditions in the structure became ventilation limited. The maximum predicted HRR was approximately 7~MW before the fire conditions became ventilation limited and started to decay. The HRR decreased to approximately 2~MW as the amount of oxygen inside the structure became limited. At this time, there was an insufficient amount of oxygen in the structure to burn all of the fuel; therefore, localized burning occured near the ventilation openings where ambient air was available.

@@

@@

As the simulated fire grows in the basement, the pressure in the basement rises and casues the hot gases to flow upwards from a region of high pressure (basement) to low pressure. Figure~\ref{fig:smv_pressure} shows the calculated pressure conditions in the structure just before and after the rear basement window failed in the simulation (342~s). The pressure rise in the basement ranges from a 5~Pa ($7.3 \times 10^{-4}$~psi) over-pressure at mid-level height to greater than 10~Pa ($1.5 \times 10^{-3}$~psi) at the ceiling. Gases at an elevated pressure will flow towards a region of lower pressure. Once the rear basement window fails, the high pressure gases flow towards the low pressure regions in the house towards the garage and front door via the stairwell.

@@

The velocity vectors shown in Fig.~\ref{fig:smv_velocity_vector} (15~s after the interior door fails) indicate the direction of flow within the structure.

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption{FDS simulated velocity vectors, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_velocity_vector}
\end{figure}

@@

% Analysis of the temperatures from the FDS simulation focuses on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell. The temperature profile at these high hazard areas is shown via several snapshots in time to illustrate the change in the interior conditions. The first snapshots are shown at a time of 129~s into the simulation, just before a firefighter opened the rear porch door (as shown in Fig.~\ref{fig:temp_129s}), and 159~s into the simulation, just before the interior door fails (as shown in Fig.~\ref{fig:temp_159s}).

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption{FDS simulated temperature vectors, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_temperature_vector}
\end{figure}

% Figure~\ref{fig:temp_129s} shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic. High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the first floor. Before the interior door fails (Fig.~\ref{fig:temp_159s}), the inflow of ambient air from the open rear door reduces the temperatures near the interior doorway, but at the same time, the HRR increases because of the additional ventilation, as shown in Fig.~\ref{fig:hrr}. As shown in Fig.~\ref{fig:temp_161s}, after the second floor interior door fails, the high temperature gas that filled the rear porch flows in the direction of lower pressure (i.e., towards the front door). Note that the conditions in the attic do not appear to change.

% As shown in Fig.~\ref{fig:temp_175s}, 15~s after the door failed, high temperature gases descended to approximately 1~m (3.28~ft) above the floor through the interior hallway and are flowing into the kitchen.

@@

\section{Simulated Stairwell Flow Path}
\label{sec:simulated_flow_path}

From on-scene reports (Section~\ref{sec:incident_summary}) and the FDS simulation results (Section~\ref{sec:temperature}), the interior conditions in the stairwell on the front side of the structure were initially tenable. The NIOSH report~\cite{NIOSH:Bowyer2} indicated that the fire was located in the basement. After the rear basement windows failed, the simulation results indicate a high-hazard area (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F) in the stairwell below the laundry room landing area. The two E26 firefighters were located within the flow path between the basement and the vent outlets on the front side of the structure.

After the rear basement windows failed, an interior flow path was created from the basement living room area and the vent outlets on the front side of the structure (the front door and the overhead garage door). The rear basement window failures resulted in a rapid change in the conditions within the flow path. After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed towards lower pressure areas via the stairwell. The arrows shown in Fig.~\ref{fig:flow_path_top} indicate the simulated flow direction of gases from the basement after the window failures. In this figure, the red arrows indicate elevated gas temperatures, and the blue arrows indicate relatively cooler gas temperatures. The arrow that transitions from red to blue indicates that the heated gases were cooling as they flowed away from the fire towards the front of the structure. The two arrows located at the door on the second floor (towards the front of the structure) indicate bi-directional flow. At that doorway, cool ambient air flowed towards the fire near the bottom of the door, and hot gases flowed away from the fire near the top of the door.

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/Flow_Path_Top}
\caption{Summary of simulated flow path in the stairwell on the basement and first floors after rear basement window failures.}
\label{fig:flow_path_top}
\end{figure}

@@

A person is susceptible to second-degree burn injuries if exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{contactburn}. Although firefighters wear protective gear, gear only offers a finite amount of protection. The polycarbonate in a self contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}. Structural fire fighting coats and pants are tested to withstand temperatures of 260~$^{\circ}$C (500~$^{\circ}$F)~\cite{nfpa2013standard}. Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him/her at risk. Exposure of equipment to temperatures of 260~$^{\circ}$C (500~$^{\circ}$F) represents a Class~III exposure~\cite{Donnelly2006}. Firefighters are at increased risk levels when encountering Class~III exposure conditions for more than 5~minutes~\cite{Donnelly2006}. Therefore, for the analysis of the simulated exposure temperatures, the maximum visualized temperature is set to indicate all values that are greater than or equal to 260~$^{\circ}$C (500~$^{\circ}$F). This means that temperatures visualized at the maximum range in the displayed model output are at a minimum of 260~$^{\circ}$C (500~$^{\circ}$F); the actual simulated temperatures could in fact be greater.

@@

@@

@@

% Door control - search then close doors
% 360 of building
% Stay out of the flow path
% Exterior attack from rear deck gun

% In this fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in highly hazardous conditions. These conditions would be equivalent to or greater than a Class~III exposure~\cite{Donnelly2006}. Prediction of the failure mode and failure time of the door is not a reasonable expectation given the large number of unknowns that the firefighters faced on the fire ground. In this case, the timing of the interior attack appears to have coincided with the failure time of the door. Research has been conducted~\cite{madrzykowski2009fire, kerber2009fire} and continues to be conducted by NIST, Underwriters Laboratories (UL), and others that demonstrates that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of firefighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure.

@@

% NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2~\sfrac{1}{2}~story single family structure in Chicago, IL, that resulted in the death the captain of a fire department. The fuel, fire size, and fire growth rate that were used in the FDS simulations were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer2}, post-incident pictures, videos, and relevant literature. This resulted in a specified source fire of 12.3~MW in the attic and rear porch of the structure. However, based on the limited ventilation conditions in the attic and enclosed porch, the FDS simulation results indicated a maximum HRR of approximately 9~MW as a result of the limited supply of oxygen.

% The fire started in the attic and spread down into the enclosed porch on the rear of the structure. The spread of fire and hot gases into the second floor of the structure was limited by a closed steel-faced, wood-framed door that was located between the enclosed porch and the hallway. After exposure to the elevated temperatures and pressure from the fire in the porch area, the wood frame of the door decomposed and the steel faces of the door failed and collapsed inward. The door failure resulted in the establishment of a flow path between the higher pressure and higher temperature conditions in the enclosed porch and the lower pressure and lower temperature conditions in the hallway and kitchen areas of the second floor. The temperature of the gases that flowed into the hallway at face height was calculated to exceed 260~$^{\circ}$C (500~$^{\circ}$F). Unfortunately, a captain and firefighter were advancing a hose line in the hallway at the time of the door failure. The captain was overcome by the rapid change in conditions before he could exit to the safety of the kitchen area. After a Mayday call, the captain was rescued from the structure but later succumbed to his injuries.

>>>>

The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards areas of lower pressure via the interior stairwell towards the front of the structure. After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell. The temperature of the gases in the interior stairwell was estimated to be in excess of 600~$^{\circ}$C (1100~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F). Unfortunately, two E26 firefighters were located in the flow path between the basement and the doors on the front side of the structure. After a Mayday call, both firefighters were removed from the structure and immediate medical treatment was provided. The two firefighters were transported to the local medical center where the lieutenant was pronounced dead and the fire fighter/paramedic died two days later.

@@

Part of the function of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response. NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas,Weinschenk:Chicago}. The objective of these studies has been to improve the safety and effectiveness of firefighters.

@@

In Fig.~\ref{fig:hrr_w_fds}, the solid line represents the HRR that was prescribed in the FDS simulation, and the dashed line represents the actual HRR that was predicted by FDS based on the ventilation conditions. From 0~s to 300~s, the predicted HRR was in agreement with the prescribed HRR because there was an adequate amount of oxygen for all of the fuel to combust. From 300~s to 342~s (the time at which the first basement window failed), the predicted HRR was lower than the prescribed HRR because the fire conditions in the structure became ventilation limited. The maximum predicted HRR was approximately 7~MW before the fire conditions became ventilation limited and started to decay. The HRR decreased to approximately 2~MW as the amount of oxygen inside the structure became limited. At this time, there was an insufficient amount of oxygen in the structure to burn all of the fuel; therefore, localized burning occurred near the ventilation openings where ambient air was available.

@@

Note that the HRR in the simulation might be overpredicted due to limitations in the combustion model related to the reignition of fuel-rich gases. In other words, there is some combustion occurring in the simulation near the front door and second floor as the fuel-rich gases mix with fresh air and reignite, which is not consistent with on-scene and post-incident photographs. However, for the high-hazard areas that are the focus of this study (the basement and interior stairwell), the pressures, temperatures, and velocities are representative of the hazardous flow path conditions that would have occurred in this fire incident.

@@

As the simulated fire grew in the basement, the pressure in the basement increased and caused the hot gases to flow upwards from a region of high pressure in the basement to a region low pressure via the interior stairwell. Figure~\ref{fig:smv_pressure} shows the calculated pressure conditions in the structure just before and after the rear basement window failed in the simulation.

In this figure, the pressure profile within the high hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions. The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed. The pressure rise in the basement ranges from a 5~Pa ($7.3 \times 10^{-4}$~psi) over-pressure at mid-level height to greater than 10~Pa ($1.5 \times 10^{-3}$~psi) at the ceiling.

@@

Gases at an elevated pressure will flow towards a region of lower pressure. Once the rear basement windows failed, the gases in the basement at an elevated temperature and pressure flowed into the interior stairwell towards the low pressure regions in the house and exhausted via the garage door and front door. The velocity contours shown in Fig.~\ref{fig:smv_velocity} indicate the magnitude of flow velocities within the structure before and after the rear basement window failures.

In this figure, the velocity profile within the high hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions. The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed.

The velocity vectors shown in Fig.~\ref{fig:smv_velocity_vectors} indicate the direction and magnitude of flow velocities within the structure before and after the rear basement window failures. Based on Figs.~\ref{fig:smv_velocity} and \ref{fig:smv_velocity_vectors}, the maximum velocity in the interior stairwell was approximately 9~m/s (20 mph).

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption{FDS simulated velocity vectors, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_velocity_vectors}
\end{figure}

@@

Analysis of the temperatures from the simulation focuses on the high hazard areas of the structure: the basement and the interior stairwell which connects the basement to the exhaust vents/doors on the front side of the structure (the front door and the garage door). The temperature contours shown in Fig.~\ref{fig:smv_temperature} indicate the gas temperatures within the structure before and after the rear basement window failures.

In this figure, The temperature profile at these high hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions. The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed.

The temperature vectors shown in Fig.~\ref{fig:smv_temperature_vectors} indicate the gas temperatures and direction of flow within the structure before and after the rear basement window failures. Based on the results shown in Figs.~\ref{fig:smv_temperature} and \ref{fig:smv_temperature_vectors} after the rear basement windows began to fail, the maximum temperature in the basement was in excess of 800~$^{\circ}$C (1500~$^{\circ}$F), and the maximum temperature in the interior stairwell was in excess of 600~$^{\circ}$C (1100~$^{\circ}$F).

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption{FDS simulated temperature vectors, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_temperature_vectors}
\end{figure}

@@

\section{Simulated Interior Stairwell Flow Path}
\label{sec:simulated_flow_path}

The NIOSH report~\cite{NIOSH:Bowyer2} indicated that the interior stairwell on the front side of the structure was used to determine that the fire was located in the basement. From the simulation results (Section~\ref{sec:temperature}), the conditions in the interior stairwell were initially tenable. After the rear basement windows failed, the simulation results indicate a high-hazard area (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F) in the stairwell near the laundry room landing area.

After the rear basement windows failed, a flow path was established between the basement living room area and the doors located on the front side of the structure (the front door and the garage door). The rear basement window failures resulted in a rapid change in the conditions within the flow path. After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell. The two E26 firefighters were located in the flow path between the basement and the doors on the front side of the structure.

The arrows shown in Fig.~\ref{fig:flow_path_top} indicate the simulated flow direction of gases from the basement after the window failures. In this figure, the red arrows indicate elevated gas temperatures, and the blue arrows indicate relatively cooler gas temperatures. The arrow that transitions from red to blue indicates that the heated gases were cooling as they flowed away from the fire towards the front of the structure. The two arrows located at the door on the second floor (towards the front of the structure) indicate bi-directional flow. At that doorway, cool ambient air flowed towards the fire near the bottom of the door, and hot gases flowed away from the fire near the top of the door.

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/Flow_Path_Top}
\caption{Summary of simulated flow path in the stairwell on the basement floor and first floor after the rear basement window failures.}
\label{fig:flow_path_top}
\end{figure}

@@

A person is susceptible to second-degree burn injuries if exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{contactburn}. Although firefighters wear protective gear, gear only offers a finite amount of protection. The polycarbonate in a self contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}. Structural fire fighting coats and pants are tested to withstand temperatures of 260~$^{\circ}$C (500~$^{\circ}$F)~\cite{nfpa2013standard}. Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him/her at risk. Exposure of equipment to temperatures of 260~$^{\circ}$C (500~$^{\circ}$F) represents a Class~III exposure~\cite{Donnelly2006}. Firefighters are at increased risk levels when encountering Class~III exposure conditions for more than 5~minutes~\cite{Donnelly2006}. Based on the simulation results shown in Section~\ref{sec:temperature}, the simulated flow path temperatures in the interior stairwell were in excess of 600~$^{\circ}$C (1100~$^{\circ}$F) and the flow velocities were approximately 9~m/s (20 mph).

% The temperature of the gases that flowed into the interior stairwell was estimated to be approximately XXX~$^{\circ}$C (XXX~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).

@@

% Insert top-down figures from SMV showing laundry room landing area temperatures.

@@

In this fire incident, the failure of the basement windows on the rear side of the structure coincided with a rapid change in the thermal conditions in the interior stairwell. The rear basement window failures resulted in the establishment of a flow path within the interior stairwell with highly hazardous conditions. These conditions would be equivalent to or greater than a Class~III exposure~\cite{Donnelly2006}.

After the primary search was conducted, closing the interior doors (i.e., door control) could have inhibited the establishment of a flow path in the interior stairwell. A 360$^\circ$ scene size-up by the arriving firefighters could have helped determine the location of the fire in the basement and identify potential flow paths within the structure. The interior stairwell acted as a chimney for hot gases in the basement to flow towards areas of lower pressure via the interior stairwell towards the front of the structure. Firefighters should avoid placing themselves within a flow path, where elevated temperatures and flow velocities can present hazardous conditions and increase the rate of heat transfer to firefighting gear via convection.

The timing of the interior attack in the basement occurred after delays in forcible entry operations on the exterior basement door. Suppression operations should be coordinated with interior operations to reduce thermal hazards related to flow paths within a structure. Ongoing research by NIST, Underwriters Laboratories (UL), and others has demonstrates that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of firefighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure~\cite{madrzykowski2009fire, kerber2009fire}.

@@

@@

NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics of a fire that occurred within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters. The fuel, fire size, and fire growth rate that were used in the FDS simulations were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer2}, post-incident pictures, and relevant literature. This resulted in a maximum specified source fire of approximately 20~MW in the basement and rear balcony of the structure. Based on the limited ventilation conditions in the basement, the FDS simulation results indicated a HRR of approximately 2~MW as a result of the limited supply of oxygen. After the rear basement windows failed, the HRR increased to approximately 32~MW before it reached a steady-state value of approximately 20~MW.

The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards areas of lower pressure via the interior stairwell towards the front of the structure. After the rear basement windows failed, a flow path was established between the basement living room area and the doors located on the front side of the structure (the front door and the garage door). The rear basement window failures resulted in a rapid change in the conditions within the flow path. After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell. The temperature of the gases in the interior stairwell was estimated to be in excess of 600~$^{\circ}$C (1100~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).

Unfortunately, two E26 firefighters were located in the flow path between the basement and the doors on the front side of the structure. After a Mayday call, both firefighters were removed from the structure and immediate medical treatment was provided. The two firefighters were transported to the local medical center where the lieutenant was pronounced dead and the fire fighter/paramedic died two days later.
